### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. While
wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features
by evaluating their usefulness to a given classifier, filter methods
evaluate feature subsets according to certain properties of features 
themselves. Within filter methods, feature selection algorithms can be
further classified into ranking methods and subset methods. The former
evaluate each feature independently, while the latter evaluate a
subset at a time \cite{brown2012conditional}. Listed below is a brief
introduction to popular feature selection algorithms that we later
compare to.

>>>>

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. Wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features by evaluating their usefulness to a given classifier, they usually produce the best results but they are computationally expensive to large data sets or to high dimensional problems. Filter methods
evaluate feature subsets according to certain properties of features 
themselves. Within filter methods, feature selection algorithms can be
further classified into ranking methods and subset methods. The former
evaluate each feature independently, while the latter evaluate a
subset at a time \cite{brown2012conditional}. Listed below is a brief
introduction to popular feature selection algorithms that we later
compare to.
